\documentclass[11pt,a4paper]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{xcolor}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \textbf{DIPRAJ DHAR}} \\
    \vspace{1pt}
    {\large Software Engineer} \\
    \vspace{2pt}
    \small
    \faIcon{phone} (+8801)533063814 $|$ 
    \faIcon{map-marker-alt} Teribazar ,Chattogram $|$
    \faIcon{envelope} dipraj2516@student.nstu.edu.bd \\
     \vspace{2pt}
    \href{https://www.linkedin.com/in/dipraj-dhar/overlay/about-this-profile/?lipi=urn%3Ali%3Apage%3Ad_flagship3_profile_view_base%3B%2B1u4I%2FnwQZ%2BnR0I8ZPuSaw%3D%3D}{\faIcon{linkedin}} \quad
    \href{https://github.com/dipgitcom}{\faIcon{github}} \quad
    \href{https://dipraj-portfolio.vercel.app/}{\faIcon{globe}}
    
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Noakhali Science and Technology University}{Mar. 2021 - Running}
{Bachelor of Science in Software Engineering}{3.46 out of 4 up to 7th semester}
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Languages:}  Python, Java, C, SQL \\
\textbf{Technologies/Frameworks:}  GitHub Desktop, Laravel \\
\textbf{Software Dev. Process:} Design Patterns, SOLID \\
\textbf{Web Dev. :} Html, Css, Javascript, Bootstrap, PHP  \\
\textbf{Soft Skills:}  Problem-solving ability, Adaptability, Communications, and Team working capability, Agile. \\
\end{tabular*}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Aspire Institute - Haravard University}{13 Feb, 2025 - 25 May, 2025}
{Leadership Program - Cohort 2}{New York, USA}
\resumeItemListStart
\resumeItem{A future where every young person achieves their full potential and contributes their leadership and talents to build thriving communities.}
\resumeItem{Experience world-class learning through Harvard case studies, discussions, and interactive sessions.}
\resumeItem{Meet and collaborate with talented peers and mentors from around the world.
}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{ServiceHub \href{https://github.com/dipgitcom/ServiceHub}{\faIcon{github}}} \emph{| Laravel, SQL, Html, Css, Js, Bootstrap, Google Maps API  }}{Mar 14, 2025 - April 15, 2025}
\resumeItemListStart
\resumeItem{ServiceHub is a Laravel-based platform connecting users with local service providers for easy booking and management.}
\resumeItem{Supports role-based dashboards for customers, providers, admins, and moderators.}
\resumeItem{Integrates Google Maps for location and Google Pay for secure payments.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{NstuQuickBill \href{https://github.com/dipgitcom/Nstu_QuickBill-A-gratuity-Billing-System-}{\faIcon{github}}} \emph{| Html, Css, Js, Bootstrap, PHP, SQL}}{Aug 10, 2024 - Dec 05, 2024}
\resumeItemListStart
\resumeItem{Digitizes bill submission and approval at Noakhali Science and Technology University.}
\resumeItem{Tracks bills through multiple sectors with status updates and verification steps.}
\resumeItem{Allows document upload, real-time tracking, and approval history display.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{NourishUnity \href{https://github.com/dipgitcom/NourishUnity}{\faIcon{github}}} \emph{| HTML, CSS, Js, Bootstrap, PHP, Google Maps API }}{Mar 10, 2024 - Sep 30, 2024}
\resumeItemListStart
\resumeItem{Collect excess edible food from farms, restaurants, supermarkets, etc., before it goes to waste.}
\resumeItem{Deliver rescued food to shelters, food banks, and low-income communities to fight hunger.
}
\resumeItem{Reduce environmental impact of food waste and raise awareness on responsible consumption.}

\resumeItemListEnd

\resumeProjectHeading
{\textbf{FaceRecognitionAttendenceSystem \href{https://github.com/dipgitcom/Face-Recognition-Attendence-System}{\faIcon{github}}} \emph{| Python, OpenCV, Numpy, Csv}}{Dec 28, 2024 - Jan 10, 2024}
\resumeItemListStart
\resumeItem{Automated Attendance using real-time face recognition via webcam.
}
\resumeItem{Stores attendance data with timestamp in a CSV file daily.}
\resumeItem{Enhanced performance with frame skipping and error logging.}
\vspace{2pt}
{\textbf{More Project(Checkout) - \href{https://github.com/dipgitcom}{\faIcon{github} Github}}

\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Major Coursework}
\resumeItemListStart
\begin{multicols}{4}
\resumeItem{Data Structures}
\resumeItem{Software Methodology}
\resumeItem{Algorithms Analysis}
\columnbreak
\resumeItem{Database Management}
\resumeItem{Artificial Intelligence}
\resumeItem{Applied Data Science}
\columnbreak
\resumeItem{Software Maintenance}
\resumeItem{Software Testing}
\resumeItem{Design Pattern}
\columnbreak
\resumeItem{Software Project Lab}
\end{multicols}
\resumeItemListEnd

\section{Certification}
\resumeItemListStart

\resumeItem{Machine Learning With Python - IBM \href{https://drive.google.com/file/d/1aKYobS76OtNgEyjMkzWw8A4h8preb5Po/view?usp=drive_link}{\faIcon{link}}}
\resumeItem{Machine Learning - Microsoft \href{https://drive.google.com/file/d/12HAHAU2V-luh4zW7fIsnPsoTSrg2G5Hb/view?usp=drive_link}{\faIcon{link}}}
\resumeItem{Google Data Analytics - Google \href{}{\faIcon{link}}}
\resumeItem{Google IT Automation with Python - Google \href{}{\faIcon{link}}}


\resumeItemListEnd

\end{document}
